### 2016-07-01 sec1_introduction.tex
Final Final Version

\begin{figure}[h]
	\vspace{-3mm}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ timestamps vary $O$} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1k$ objects vary $T$}
    \label{fig:fig2}
    \end{subfigure}
    \vspace{-2mm}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with up two 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

@@

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we replicate the snapshots in multiple data chunks to support efficient parallel processing. Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework as a fine-granularity partitioning strategy to achieve workload balance. For each star, an Apriori Enumerator is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions of
temporal points. 
The results show that both our parallel scheme efficiently supports GCMP mining in large datasets.
In particular, with near 200 million trajectory points, 
SPARE runs in 12 minutes using 162 cores, whereas
centralized solutions take from 10 to 30 hours.
Moreover, our optimized SPARE methods achieves upto 14 times efficiency
as compared to the baseline algorithm with almost linear scalability.

>>>>

\begin{figure}[h]
	\vspace{-3mm}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{\small Varying No. of objects} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{\small Varying No. of timestamps}
    \label{fig:fig2}
    \end{subfigure}
    \vspace{-2mm}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with up two 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

@@

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we design a baseline solution by replicating the snapshots in multiple data chunks to support effective parallel mining. Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework to resolve limitations of the baseline. SPARE achieves workload balance by partitioning objects into fine granular stars.  For each star partition, an Apriori Enumerator is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated in SPARE.

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions of
temporal points. 
The results show that both our parallel schemes efficiently support GCMP mining in large datasets.
In particular, with over 170 million trajectory points,
SPARE achieves upto 112 times speedup using 162 cores as compared to the state-of-the-art centralized schemes.
Moreover, SPARE further achieves upto 14 times efficiency
as compared to the baseline algorithm with almost linear scalability.

### 2016-07-01 sec6_experiment.tex
Final Final Version

\subsection{Analysis of SPARE framework}
In this part, we extensively evaluate the advantage brought by the
sequence simplification and load balancing techniques.

@@

\subsection{Scalability}
Finally, we examine the scalability of our proposed frameworks in two contexts. 
First, we use the single-node mode and examine the performance with multi-cores. 
We also compare it with the state-of-the-art solutions for swarm and platoon patterns 
since they were designed to run in a centralized server. 
Second, we examine the pattern detection time with increasing computing resources (number of machines). 
As the poor performances of swarm and platoon, we only use 60\% of each dataset for experiments. 
The results are reported in Figure~\ref{exp:scalability}. 
First, the centralized schemes are not suitable to discover patterns in 
large-scale trajectory databases. It takes nearly $30$ hours to 
detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
In contrast, when utilizing the multi-core environment, 
SPARE achieves $9$ times speed up compared to \emph{platoon} and $22$ times speed up compared to \emph{swarm}. 
%our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
Second, we see that both TRPM and SPARE demonstrate promising scalability in terms of the number of machines available. The running time almost decreases inversely as more machines are used. 
When there are $11$ nodes in the cluster, 
SPARE achieves at most $63$ times faster 
than \emph{platoon} and at most $170$ times better than \emph{swarm}.
%state-of-the-art \emph{platoon} detector in a centralized server.

>>>>

\subsection{Analysis of SPARE framework}
In this part, we extensively evaluate SPARE from three aspects:
(1) the advantages brought by the sequence simplification, (2) the effectiveness of load balance, and (3) the scalability with increasing computing resources.
%Then, we study the scalability of SPARE with increasing computing resources.

@@

\subsubsection{Scalability}
When examining SPARE with increasing computing resources (number of machines), we also compare SPARE with the state-of-the-art solutions for \emph{swarm} and \emph{platoon} in the single-node setting. Since the original \emph{swarm} and \emph{platoon} detectors cannot handle very large-scale datasets, we only use 60\% of each dataset for evaluation. To make fair comparisons, we customize two variants of SPARE to mine \emph{swarm}s and \emph{platoon}s, which are denoted as SPARE-S and SPARE-P respectively. The customization is according to the settings in Table~\ref{tbl:patterns} and the results are reported in Figure~\ref{exp:scalability}. 
First, the centralized schemes are not suitable to discover patterns in 
large-scale trajectory databases. It takes nearly $30$ hours to 
detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
In contrast, when utilizing the multi-core environment, 
SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 
%our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
Second, we see that SPARE schemes demonstrate promising scalability in terms of the number of machines available. The running times decrease almost inversely as more machines are used. 
When all the $11$ nodes ($162$ cores) are available, 
SPARE-P is upto $65$ times and SPARE-S is upto $112$ times better than the state-of-the-art centralized schemes.
%than \emph{platoon} and SPARE-S is upto $112$ times better than \emph{swarm}.
%state-of-the-art \emph{platoon} detector in a centralized server.
